---
title: "R Notebook"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

### Packages 

```{r}
library(tidyverse)
library(xlsx)
library(WDI)
library(rvest)
library(reshape2)
library(glue)
```


### I downloaded the data from evds (CBTR database)

```{r}
colnames1 <- c(
  "Date",
  "Current_Accounts_MilUS",
  "Export_MilUS",
  "Import_MilUS",
  "Reserve_Assets_MilUS",
  "FDI_Net_Assets_MilUS",
  "Portfolio_Net_Assets_MilUS")

df1 <- read.xlsx("df1.xlsx", sheetIndex = 1, endRow = 430)
colnames(df1) <- colnames1
df1 <- df1 %>%
  mutate(Date = as.Date(paste0(df1$Date, "-01"), format = "%Y-%m-%d"))
df1
```

```{r}
colnames2 <- c(
  "Date",
  "BS_Reserve",
  "BS_Cental_Bank",
  "BS_Banks",
  "Total_Assets",
  "Deposit")

df2 <- read.xlsx("df2.xlsx", sheetIndex = 1, endRow = 417)
colnames(df2) <- colnames2
df2 <- df2 %>%
  mutate(Date = as.Date(paste0(df2$Date, "-01"), format = "%Y-%m-%d"))
df2
```



### Datas from World Bank

```{r}
TR_WDI_Download <- WDI(country = "TR",
    indicator = c(
      "TX.MNF.TECH.ZS.UN",
      "TM.TAX.MANF.SM.AR.ZS",
      "SI.POV.GINI",
      "NE.RSB.GNFS.ZS",
      "VC.IHR.PSRC.MA.P5",
      "IC.FRM.BNKS.ZS",
      "IC.BUS.EASE.XQ",
      "FM.LBL.BMNY.ZG",
      "FB.CBK.DPTR.P3",
      "NE.TRD.GNFS.ZS",
      "NE.CON.GOVT.CN",
      "FR.INR.LEND",
      "DT.DOD.DSTC.IR.ZS",
      "GC.DOD.TOTL.GD.ZS",
      "GC.TAX.TOTL.CN",
      "FP.CPI.TOTL.ZG",
      "FD.RES.LIQU.AS.ZS",
      "NY.GNS.ICTR.GN.ZS",
      "DT.DOD.DIMF.CD",
      "BN.KLT.DINV.CD",
      "BM.KLT.DINV.CD.WD",
      "NY.GDP.PCAP.CD",
      "NV.IND.MANF.ZS",
      "FD.AST.PRVT.GD.ZS",
      "NE.EXP.GNFS.ZS"),
    start = 1960,
    end = 2019
    )
TR_WDI <- TR_WDI_Download[,-c(1,2)]
colnames_WDI <- c(
  "Years",
  "Med_High_Exports",
  "Tariff_Rate",
  "Gini_Index",
  "External_Balance_on_Goods_Services_%GDP",
  "Homicides",
  "Firms_Using_Banks(%firms)",
  "Ease_of_Doing_Business",
  "Money_Growth",
  "No_Depositors",
  "Trade(%GDP)",
  "Gov_Final_Consumption",
  "Lending_Interest_Rate",
  "Short_Term_Debt(%Reserves)",
  "Gov_Debt_Total(%GDP)",
  "Tax_Revenue",
  "Inflation_Consumer",
  "Liquid_Reserve_Ratio(%)",
  "Gross_Savings(%GNI)",
  "IMF_Credit",
  "FDI_Net",
  "FDI_Net_Outflows",
  "GDP",
  "Manufacturing%",
  "Credit_Private",
  "Export%")
colnames(TR_WDI) <- colnames_WDI

```

### Maddison Table, I picked this version because it contains World's GDP overall

```{r}
Mad <- read_csv("md.csv")
Mad$GDP <- Mad$`Real GDP per capita in 2011US$, multiple benchmarks (Maddison Project Database (2018))`
Mad <- Mad %>%
  select(-`Real GDP per capita in 2011US$, multiple benchmarks (Maddison Project Database (2018))`)
Mad
```


### Maddison comparison dataframe

```{r}
Mad_Comparison <- Mad %>% 
  filter(Entity %in% c("Turkey","World"),
         Year > 1949) %>%
  mutate(Era = case_when(
    Year < 1960 ~ "50's",
    Year < 1970 ~ "60's",
    Year < 1980 ~ "70's",
    Year < 1990 ~ "80's",
    Year < 2000 ~ "90's",
    Year < 2010 ~ "00's",
    Year < 2020 ~ "10's"),
    Era = as.factor(Era, order = c("50's","60's","70's","80's","90's","00's","10's")))
```




### Web scraping function for ekodialog.com

```{r}
ekodialog_scraper <- function(stat_name){
  url <- glue("https://www.ekodialog.com/istatistik/{stat_name}.html") %>% as.character()
  df_list <- read_html(url) %>%
  html_table(fill = T)
  df <- df_list[[14]] 
  return(df)
}
```


### Exchange Rate

```{r}
df <- ekodialog_scraper("doviz_kur")
df <- df[-c(1:4),]
colnames(df) <- c(
  "Year",
  "Average_USD",
  "Average_Mark",
  "Average_Euro")
df <- df[,c(1:4)]

# USD tidy
df$Average_USD[c(19:35)]
v <- gsub("\\.", "",df$Average_USD[c(19:35)])
v <- gsub(",", "\\.",v)
df$Average_USD[c(19:35)] <- v

# Mark tidy
df$Average_Mark[c(20:32)]
v <- gsub("\\.", "",df$Average_Mark[c(20:32)])
v <- gsub(",", "\\.",v)
df$Average_Mark[c(20:32)] <- v

# Euro tidy
df$Average_Euro[c(30:35)]
v <- gsub("\\.", "",df$Average_Euro[c(30:35)])
v <- gsub(",", "\\.",v)
df$Average_Euro[c(30:35)] <- v

df[df == "-"] <- NA
df <- sapply(df, as.numeric) %>% as.data.frame()
(exchange_rates <- df)

```


### Inflation

```{r}
df <- ekodialog_scraper("enflasyon")
colnames(df) <- c(
  "Year",
  "Wholesale_Price_End_Year",
  "Wholesale_Price_Average",
  "Consumer_Prices_End_Year",
  "Consumer_Prices_Average")
df <- df[-c(1:3),]
df <- sapply(df, as.numeric) %>% as.data.frame()
(inflation_ed <- df)

```


### Foreign_Investment

```{r}
# Foreign_Investment
df <- ekodialog_scraper("yabanci_ser")
df <- df[-c(1:4),-c(3)]
colnames(df) <- c(
  "Year",
  "Permits",
  "Realisations")
df[25,2] <- "1.208"
df[26,2] <- NA
df <- sapply(df, as.numeric) %>% as.data.frame()
(foreign_capital <- df)
write_csv(foreign_capital, "foreign_capital.csv")

```


### Reserves

```{r}
df <- ekodialog_scraper("mb_rezerv")
colnames(df) <- c(
  "Months",
  1996:2005
)

df <- df[-c(1,2), -c(1,11)]
df$Months = month.name
df <- df %>% melt()
colnames(df) <- c(
  "Month",
  "Year",
  "CRBT_RESERVE_OF_DOLAR")
(reserve <- df)

```

### Interest Rates

```{r}
df <- ekodialog_scraper("faiz_oranlar")
df <- df[-c(1:4),]
colnames(df) <- c(
  "Year",
  "Saving_Deposits_Int_Rates",
  "Int_Rates_on_CBRT_Disc",
  "Interbank_Overnight_Rate")
df[df == "-"] <- NA
df$Int_Rates_on_CBRT_Disc <- gsub(",", "\\.",df$Int_Rates_on_CBRT_Disc)
df[35,2] <- "22.1"
df[35,4] <- "19.1"
df <- sapply(df, as.numeric) %>% as.data.frame()
(interest_rates <- df)

```

### Oecd reserves

```{r}
read_csv("oecd_all.csv") %>% 
  filter(LOCATION == "TUR") %>%
  select(INDICATOR) %>%
  unique()


```

### An attempt to capture people's opinions about the crisis 


```{r}
library(rvest)
library(glue)



entry <- list()
date <- list()
author <- list()
for (i in c(1:6)) {     
url <- glue("https://eksisozluk.com/21-subat-krizi--386798?p={i}") %>%
  as.character()
entry[[i]] <- read_html(url) %>%
  html_nodes(".content") %>%
  html_text()
date[[i]] <- read_html(url) %>%
  html_nodes(".permalink") %>%
  html_text()
author[[i]] <- read_html(url) %>%
  html_nodes(".entry-author") %>%
  html_text()}



```
































